\newcommand{\BF}[1]{\bf \sffamily \large #1 \normalsize \normalfont }
__SECT2 { __NEW{ICS WEB Tool Guide } 
\label{sec:ICSWEBToolGuide} }
The ICS(Incident Command System) WEB Tool is an WEB based tool to: 
\begin{itemize}
\item help organize and increase functionality of untrained personnel
\item track ICS personnel and response teams
\item report and maintain status of Damage Assessments
\item communicate between ICS personnel
\item keep records of communications, Damage Assessments, personnel actions
\end{itemize}
----------------------------------------------------------------------------

\BF{Accessing ICS WEB Tool}
\begin{itemize}
\item Using WEB Browser go to: __COMMENT{ http://63.199.179.155/WEBTool }
\item The ( username / password ) is ( __COMMENT{emprep / user101} )
\end{itemize}

\BF{Signing In}--
All ICS personnel must __COMMENT{Sign-In} in order to properly use the Tool.
\newline
**Please assist anyone without WEB access to __COMMENT{Sign-In}  as well.
During Emergencies and Drills some people will not have smartphones or laptops.
\begin{itemize}
\item From the ICS WEB Tool menu select __COMMENT{Sign-In}
\item Search for your name by entering part of your name (__COMMENT{Enter Name})
and pushing (__COMMENT{FindByName}).
\item If you see your name, __COMMENT{Select} it,
otherwise click __COMMENT{New Name}
\item Edit/Enter  __COMMENT{Name}, __COMMENT{Skills}, and __COMMENT{Assignment} in the displayed form as needed.
If you know your ICS Assignment, assign yourself here.
\item Push (__COMMENT{Sign In}) to Sign In.
\item All Personnel information can be displayed and editted 
from any Personnel Section tools.
\end{itemize}



\BF{View ICS Staffing}
\begin{itemize}
\item From the ICS WEB Tool menu 
select __COMMENT{Personnel Info} 
\item This will display all ICS Personnel and their assignments.
\item To edit individual Personnel information select the 
__COMMENT{Name} and push __COMMENT{Edit Info}.
This will take you to the 
__COMMENT{Personnel--Edit Information}.
This form is used by ICC staff to make ICS Assignments.
\item Remember to push __COMMENT{SAVE}.
\item From here you can also display Personnel grouped by skills 
( __COMMENT{Group By Skill} ) 
or
display the general ICS Assignments (__COMMENT{List By Role})
\end{itemize}

\BF{View Personnel Grouped by Skill}
\begin{itemize}
\item From the ICS WEB Tool menu 
select __COMMENT{Personnel By Skill} 
to display Personnel Grouped by Skill.
\item To edit individual Personnel Assignment select the __COMMENT{Name} and 
push ( __COMMENT{Edit Info} )
\item To display ICS Assignment 
push ( __COMMENT{List By Role } )
\end{itemize}

\BF{View Personnel ICS Assignments}
\begin{itemize}
\item From the ICS WEB Tool menu 
select __COMMENT{Assignments / Deployment} 
\item View/Edit individual Personnel information by pushing the (__COMMENT{Name})
\item View and edit Damage Status at the Address where a Team is deployed 
push the (__COMMENT{Address})
\end{itemize}

\BF{Reporting Damages}
\begin{itemize}
\item From the ICS WEB Tool menu select __COMMENT{Damages By Address}
\item Select __COMMENT{Street Name} of damage.
\item Select __COMMENT{Address} of damage.
\item On the Damage Status form 
enter 
__COMMENT{Damage Assessments} for __COMMENT{Fire, Hazards, Structures, and People}.
\item Response Team deployment is indicated here.  
Only available teams will be displayed in the menu.
Available teams are teams that are not already deployed 
and with at least two member assigned.
Use the Personnel section to form teams.
\item Add details in the __COMMENT{Notes} section.
\item Identify yourself at the __COMMENT{Reporter} menu 
\item Push __COMMENT{Save} (very important)
\item Verify in __COMMENT{Change History} the information you entered.
\end{itemize}

\BF{Viewing Damage Status Summary}
\begin{itemize}
\item From the ICS WEB Tool menu select __COMMENT{Damages By Category}.
\item Select from the different Categories.  
__COMMENT{NewestFive} (newest five reports) and 
__COMMENT{UnresolvedDamages} will generally be the most useful.
\item Selecting any of these choices will display the Addresses
and their unresolved issues and their Response Team deployment.
\item Clicking the Address will bring up its Damage Status form 
which can be editted (See Reporting Damages above.).
\item Use the __COMMENT{Refresh} button to update the display.
\item __COMMENT{Category Menu} takes you back to the  __COMMENT{Damages By Category} menu.
\end{itemize}

\BF{Changing Damage Status or Response Team Deployment}
\begin{itemize}
\item From the ICS WEB Tool menu select 
__COMMENT{Damages By Address} or __COMMENT{Damages By Category}
\item Navigate to an Address as per __COMMENT{Damage By Address}
or __COMMENT{Damage By Category}
\item Continue as per __COMMENT{Reporting Damages} above.
\end{itemize}

\BF{Viewing Messages}
\begin{itemize}
\item From the ICS WEB Tool menu select (__COMMENT{Messaging})
\item Select message recipients in the __COMMENT{Message To} menu.
\item Push (__COMMENT{Display}) to display messages to those selected.
\item Push __COMMENT{Send Message} to go to Send Message Form
\end{itemize}

\BF{Sending Messages}
\begin{itemize}
\item From the ICS WEB Tool menu select __COMMENT{Messaging} 
\item Select the originator of message (__COMMENT{From}) 
\item Select message recipients with the __COMMENT{Message To} form.
\item Select the __COMMENT{Location} that the message refers.
\item __COMMENT{Compose Message} from pre-defined statements. 
\item Add details in the __COMMENT{Additional Informatiion} form.
\item Push __COMMENT{SEND}.
\end{itemize}
\BF{The following is a list of the different ICS Roles 
with a list of tools they would find useful.}
\begin{itemize}
\item \BF{Incident Commander}
\begin{itemize}
\item __COMMENT{Damages By Category} to monitor Damage status
\item __COMMENT{Assignments / Deployment} to monitor Team status
\item __COMMENT{Messaging}
\end{itemize}
\item \BF{Radio Operator}
\begin{itemize}
\item __COMMENT{Sign In} to Sign In people via walkie-talkie
\item __COMMENT{Damages By Address} to enter Damage information via walkie-talkie
\item __COMMENT{Personnel Info} to enter informaiton via walkie-talkie
\item __COMMENT{Assignments / Deployment} to enter informaiton via walkie-talkie
\item __COMMENT{Messaging} to enter messages transmitted via walkie-talkie
\end{itemize}
\item \BF{Scribe }
\begin{itemize}
\item __COMMENT{Damages By Category} to update Status Board
\item __COMMENT{Damages By Address} to enter information via runners
\item __COMMENT{Messaging}
\end{itemize}
\item \BF{Logistic Captain}
\begin{itemize}
\item __COMMENT{Find Equipment in Neighborhood}
\item __COMMENT{Damages By Category} to determine equipment needs
\item __COMMENT{Messaging} to receive Supply requests
\end{itemize}
\item \BF{Response Team Captain}
\begin{itemize}
\item __COMMENT{Damages By Category} to monitor Damage status
\item __COMMENT{Assignments / Deployment} to assemble Teams and record Team deployment
\item __COMMENT{Damages By Address} to record Team deployment
\item __COMMENT{Personnel Info} to assemble Teams
\item __COMMENT{Messaging} to send instruction and receive status from Teams
\end{itemize}
\item \BF{Response Teams }
\begin{itemize}
\item __COMMENT{Damages By Address} to record Damage status
\item __COMMENT{Messaging} to send requests and receive instructions
\end{itemize}

\item \BF{Division Captain}
\begin{itemize}
\item __COMMENT{Sign In} to Sign In people at Assembly Point
\item __COMMENT{Damages By Address} to record Damage Assessments
\item __COMMENT{Messaging}
\end{itemize}
\item \BF{Block Captains / Damage Assessors}
\begin{itemize}
\item __COMMENT{Damages By Address} to record Damage Assessments
\item __COMMENT{Messaging}
\end{itemize}
\end{itemize}

